SMT-Boosted Security Types for Low-Level MPC

### 2025-11-11 toplas26/metaty.tex
checkpoint

\begin{definition}[$\metaprot$ Type Checking Judgements]
  \emph{Type checking judgements} are of the syntactic form
  $\shtrip{\Gamma, R, \xdefs}{\cmd}{\Gamma, R, \xdefs}$
  where $\xdefs : \phi \rightarrow \phi$ are called
  \emph{definitions}.
\end{definition}

>>>>

Type checking judgements for typing annotations are defined as follows.
The \emph{definitions} element $\xdefs$ of judgements is an environment
of SMT equivalences induced either by the program or by annotation. 
\begin{definition}[$\metaprot$ Type Checking Judgements]
  \emph{Type checking judgements} are of the syntactic form
  $\shtrip{\Gamma, R, \xdefs}{\cmd}{\Gamma, R, \xdefs}$
  where $\xdefs : \phi \rightarrow \phi$ are called
  \emph{definitions}.
\end{definition}

All typing judgements are dependent on closed expressions $e$ which we
equate up to evaluation. Since the semantics of expressions is total,
we simply evaluate expressions in preconditions of derivation
rules. The derivation rules for annotations $\sta$ are given in Figure
\ref{fig-shtripsta}. First, we note that the \TirName{Coerce} rule
extends definitions to include the equivalence specified by the $e_1
\kwas e_2$ annotation form-- we assume the validity of the equivalence
is enforced by Hoare triple verification and so is not checked (again)
here.  These definitions extend or even overwrite variable definitions
established by the protocol itself (see the \TirName{Defn} rule in
Figure \ref{fig-shtripcmd} discussed below).

In the rules for share type annotations of the form $\notg{\stt} :
\sty$,

\subsubsection{Functions and Application}
